Clustering exploration for `r params$sample_id`

### 2024-09-05 analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd
Add to PR #750

The aim is to explore the clustering and label transfers for the sample `r param$sample_id`.

@@

library(SCpubr)             # for plotting 
library(tidyverse)
library(patchwork)
library(msigdbr)
library(enrichplot)
library(clusterProfiler)
library(org.Hs.eg.db)
library(ggalluvial)

set.seed(params$seed)
```

@@

### Load the pre-processed `Seurat` object
```{r load, message=FALSE, warning=FALSE}
# open the processed rds object
srat <- readRDS(file.path(result_dir, paste0("02b-fetal_kidney_label-transfer_",params$sample_id,".Rds")))
DefaultAssay(srat) <- "SCT"

### Functions

@@

## Analysis content

@@

```{r fig.width=10, fig.height=4, out.width='100%'}
visualize_metadata(srat, meta = "Phase", group.by = "seurat_clusters")
```

```{r fig.width=8, fig.height=2.5, out.width='100%'}
visualize_metadata(srat, meta  = "S.Score", group.by = "seurat_clusters")
visualize_metadata(srat, meta = "G2M.Score", group.by = "seurat_clusters")
```

@@

```{r fig.width=8, fig.height=2.5, out.width='100%'}
for(feature in CellType_metadata$ENSEMBL_ID[CellType_metadata$ENSEMBL_ID %in% rownames(srat@assays$SCT)]){
   print(visualize_feature(srat, features = feature, group.by = "seurat_clusters"))
}
```

@@

```{r fig.height=2.5, fig.width=8, warning=FALSE, out.width='100%'}
srat <- MSigDB_score(object = srat , category = "H", gs_name = "HALLMARK_P53_PATHWAY", name = "TP53_score")
visualize_metadata(srat, meta = "TP53_score1", group.by = "seurat_clusters" )
```

@@

```{r fig.height=2.5, fig.width=8, warning=FALSE, out.width='100%'}
srat <- MSigDB_score(object = srat , category = "H", gs_name = "HALLMARK_DNA_REPAIR", name = "DNA_repair_score")
visualize_metadata(srat, meta = "DNA_repair_score1", group.by = "seurat_clusters" )
```

@@

```{r fig.height=2.5, fig.width=8, warning=FALSE, out.width='100%'}
srat <- MSigDB_score(object = srat , category = "C3", gs_name = "DROSHA_TARGET_GENES", name = "DROSHA_score")
visualize_metadata(srat, meta = "DROSHA_score1", group.by = "seurat_clusters" )
```

@@

```{r fig.height=2.5, fig.width=8, warning=FALSE, out.width='100%'}
srat <- MSigDB_score(object = srat , category = "C3", gs_name = "DICER1_TARGET_GENES", name = "DICER1_score")
visualize_metadata(srat, meta = "DICER1_score1", group.by = "seurat_clusters" )
```

@@

In addition to the list of known marker genes, we used an unbiased approach to find transcripts that characterized the different clusters.
We run DElegate::FindAllMarkers2 to find markers of the different clusters and manually check if they do make sense. 
DElegate::FindAllMarkers2 is an improved version of Seurat::FindAllMarkers based on pseudobulk differential expression method. 
Please check the preprint from Chistoph Hafemeister: https://www.biorxiv.org/content/10.1101/2023.03.28.534443v1
and tool described here: https://github.com/cancerbits/DElegate

@@

```{r fig.width=10, fig.height=10, out.width='100%'}
feature_conversion <- srat@assays$RNA@meta.data
de_results   <- DElegate::FindAllMarkers2(srat, group_column = "seurat_clusters")
#filter the most relevant markers
s.markers <- de_results[de_results$padj < params$padj_thershold & de_results$log_fc > params$lfc_threshold & de_results$rate1 > params$rate1_threshold,]
# add gene symbol for easiest interpretation of the result
s.markers$gene_ids <- s.markers$feature
s.markers <- left_join(s.markers,feature_conversion, by = c( "gene_ids") )
identical(s.markers$feature, s.markers$gene_ids)     # check the quality of the merge, must be true
DT::datatable(s.markers, caption = ("marker genes"), 
              extensions = 'Buttons', 
              options = list(  dom = 'Bfrtip',
                               buttons = c( 'csv', 'excel')))
# Select top 5 genes for heatmap plotting
s.markers <- na.omit(s.markers)
s.markers %>%
    group_by(group1) %>%
    top_n(n =  5, wt = log_fc) -> top5
# subset for plotting
cells <- WhichCells(srat, downsample = 100)
ss <- subset(srat, cells = cells)
ss <- ScaleData(ss, features = top5$feature)
p1 <- SCpubr::do_DimPlot(srat, reduction="umap", group.by = "seurat_clusters", label = TRUE, repel = TRUE) + ggtitle("Seurat Cluster - umap")
p2 <- DoHeatmap(ss, features = top5$feature,  cells = cells, group.by = "seurat_clusters") + NoLegend() + 
  scale_fill_gradientn(colors =  c("#01665e","#35978f",'darkslategray3', "#f7f7f7", "#fee391","#fec44f","#F9AD03")) 
p3 <- ggplot(srat@meta.data, aes(seurat_clusters, fill = seurat_clusters)) + geom_bar() + NoLegend()
common_title <- sprintf("Unsupervised clustering %s, %d cells", srat@meta.data$orig.ident[1], ncol(srat))
show((((p1 / p3) + plot_layout(heights = c(3,2)) | p2) ) + plot_layout(widths = c(1, 2)) + plot_layout(heights = c(3,1)) + plot_annotation(title = common_title))
DT::datatable(top5[, c(1, 9, 11, 12)], caption = ("top 5 marker genes"), 
              extensions = 'Buttons', 
              options = list(  dom = 'Bfrtip',
                               buttons = c( 'csv', 'excel')))
```

@@

```{r fig.width=15, fig.height=8, out.width='100%'}

@@

```{r fig.width=15, fig.height=10, out.width='100%'}
visualize_metadata(srat, meta = "singler_celltype_annotation", group.by = "seurat_clusters")
```

@@

```{r fig.width=15, fig.height=10, out.width='100%'}
visualize_metadata(srat, meta = "cellassign_celltype_annotation", group.by = "seurat_clusters")
```

@@

```{r fig.width=15, fig.height=10, out.width='100%'}
visualize_metadata(srat, meta = "fetal_full_predicted.organ", group.by = "seurat_clusters")
visualize_metadata(srat, meta = "fetal_full_predicted.annotation.l1", group.by = "seurat_clusters")
visualize_metadata(srat, meta = "fetal_full_predicted.annotation.l2", group.by = "seurat_clusters")
```

@@

```{r fig.width=15, fig.height=10, out.width='100%'}
visualize_metadata(srat, meta = "fetal_kidney_predicted.compartment", group.by = "seurat_clusters")
visualize_metadata(srat, meta = "fetal_kidney_predicted.cell_type", group.by = "seurat_clusters")
```

@@

```{r fig.width=15, fig.height=15, out.width='100%'}

@@

```{r fig.width=15, fig.height=15, out.width='100%'}
p1 <- SCpubr::do_AlluvialPlot(sample = srat,
                            first_group = "fetal_kidney_predicted.compartment",
                            last_group = "seurat_clusters",
                            repel = TRUE,

@@

p2 <- SCpubr::do_AlluvialPlot(sample = srat,
                            first_group = "fetal_full_predicted.annotation.l1",
                            last_group = "seurat_clusters",
                            repel = TRUE
                            )

p3 <- SCpubr::do_AlluvialPlot(sample = srat,
                            first_group = "singler_celltype_annotation",
                            last_group = "seurat_clusters",
                            repel = TRUE
                            )

p4 <- SCpubr::do_AlluvialPlot(sample = srat,
                            first_group = "cellassign_celltype_annotation",
                            last_group = "seurat_clusters",
                            repel = TRUE
                            )

(p1|p2)/(p3|p4)
```
```{r fig.width=10, fig.height=15, out.width='100%'}
SCpubr::do_AlluvialPlot(sample = srat,
                            first_group = "fetal_kidney_predicted.compartment",
                            last_group = "fetal_full_predicted.annotation.l1",
                            repel = TRUE

SCpubr::do_AlluvialPlot(sample = srat,
                            first_group = "fetal_kidney_predicted.cell_type",
                            last_group = "fetal_full_predicted.annotation.l2",
                            repel = TRUE
                                                        )

>>>>

The aim is to explore the clustering and label transfers for the sample `r params$sample_id`.

@@

library(SCpubr)             # for plotting 
library(tidyverse)
library(patchwork)
library(msigdbr)
library(enrichplot)
library(clusterProfiler)
library(org.Hs.eg.db)
library(ggalluvial)
library(ggsankey)
set.seed(params$seed)
```

@@

## Functions

@@

#### do_SankeyPlot

`do_SankeyPlot` is largely inspired by the source code from `SCpubr` as the function has been removed from the package.
https://github.com/enblacar/SCpubr/blob/v1.1.2-dev-stable/R/do_SankeyPlot.R

- `first_group` is a metadata variable. First group of nodes of the sankey plot.
- `last_group` is a metadata variable. Last group of nodes of the sankey plot.
- `middle_groups` is a metadata variable. Vector of groups of nodes of the sankey plot.
- `type` is a type of plot to make. One of:

  - `sankey`: Generates a sankey plot.
  - `alluvial`: Generated an Alluvial plot, a kind of sankey plot where all groups have the same height.

- `width` Width of the nodes.
- `space` Vertical space between the nodes. It appears to be equal to a single cell. Use big numbers to see a difference (like, 1000 or 10000).
- `position` GGplot2 position.
- `node.fill` Color to fill the nodes.
- `node.color` Color for the contour of the nodes.
- `flow.alpha` Alpha of the connections.
- `flow.color` Color for the contour of the connections.
- `text_size` Size of the labels.
- `text_color` Color of the labels.
- `smooth` How smooth the connections are.
- `use_labels` Whether to use labels or text for the node names.
- `hjust` General hjust for the labels.

```{r }

do_SankeyPlot <- function(sample,
                          first_group,
                          last_group,
                          type = "sankey",
                          middle_groups = NULL,
                          width = 0.1,
                          space = ifelse(type == "sankey", 0.05 * ncol(sample), 0),
                          position = "identity",
                          node.fill = "white",
                          node.color = "white",
                          flow.alpha = 0.75,
                          flow.color = "black",
                          text_size = 3,
                          text_color = "black",
                          font.size = 18,
                          font.type = "sans",
                          smooth = 8,
                          use_labels = FALSE,
                          hjust = NULL,
                          colors.first = NULL,
                          colors.middle = NULL,
                          colors.last = NULL,
                          plot.title = NULL,
                          plot.subtitle = NULL,
                          plot.caption = NULL){

  # Check logical parameters.
  logical_list <- list("use_labels" = use_labels)
  # Check numeric parameters.
  numeric_list <- list("width" = width,
                       "space" = space,
                       "flow.alpha" = flow.alpha,
                       "text_size" = text_size,
                       "font.size" = font.size,
                       "smooth" = smooth,
                       "hjust" = hjust)
  # Check character parameters.
  character_list <- list("first_group" = first_group,
                         "last_group" = last_group,
                         "middle_groups" = middle_groups,
                         "type" = type,
                         "position" = position,
                         "node.color" = node.color,
                         "flow.color" = flow.color,
                         "text_color" = text_color,
                         "font.type" = font.type,
                         "colors.first" = colors.first,
                         "colors.middle" = colors.middle,
                         "colors.last" = colors.last,
                         "node.fill" = node.fill,
                         "plot.title" = plot.title,
                         "plot.subtitle" = plot.subtitle,
                         "plot.caption" = plot.caption)

  `%>%` <- magrittr::`%>%`

  data <- suppressWarnings({sample@meta.data %>%
                            dplyr::select(dplyr::all_of(c(first_group, middle_groups, last_group))) %>%
                            tibble::rownames_to_column(var = "cell") %>%
                            dplyr::select(-.data$cell) %>%
                            ggsankey::make_long(dplyr::all_of(c(first_group, middle_groups, last_group))) %>%
                            dplyr::rowwise() %>%
                            dplyr::mutate(hjust = if(.data$x %in% middle_groups){0.5}
                                          else if (.data$x == last_group){0}
                                          else if (.data$x == first_group){1})})
  if (!is.null(hjust)){data$hjust <- hjust}

  colors.first <- SCpubr::do_ColorPalette(colors.use = "steelblue",
                        n = length(unique(sample@meta.data[, first_group])))
    if (is.factor(sample@meta.data[, first_group])){
      names(colors.first) <- levels(sample@meta.data[, first_group])
    } else {
      names(colors.first) <- sort(unique(sample@meta.data[, first_group]))
    }

  colors.last <- SCpubr::do_ColorPalette(colors.use = "steelblue",
                        n = length(unique(sample@meta.data[, last_group])))
    if (is.factor(sample@meta.data[, last_group])){
      names(colors.last) <- levels(sample@meta.data[, last_group])
    } else {
      names(colors.last) <- sort(unique(sample@meta.data[, last_group]))
    }

  colors.use <- c(colors.first, colors.last)
  func_use <- ifelse(isTRUE(use_labels), ggsankey::geom_sankey_label, ggsankey::geom_sankey_text)

  p <- data %>%

       ggplot2::ggplot(mapping = ggplot2::aes(x = .data$x,
                                              next_x = .data$next_x,
                                              node = .data$node,
                                              next_node = .data$next_node,
                                              fill = factor(.data$node),
                                              label = .data$node,
                                              hjust = .data$hjust)) +
       ggsankey::geom_sankey(flow.alpha = flow.alpha,
                             node.color = node.color,
                             node.fill = node.fill,
                             color = flow.color,
                             width = width,
                             position = position,
                             type = type,
                             space = space) +
       func_use(size = text_size,
                color = text_color,
                fontface = "bold",
                position = position,
                type = type,
                space = space) +
       ggplot2::scale_fill_manual(values = colors.use) +
       ggplot2::xlab("") +
       ggplot2::ylab("") +
       ggplot2::labs(title = plot.title,
                     subtitle = plot.subtitle,
                     caption = plot.caption) +
       ggplot2::theme_minimal(base_size = font.size) +
       ggplot2::theme(axis.title = ggplot2::element_text(color = "black",
                                                         face = "bold"),
                      axis.line.x = ggplot2::element_blank(),
                      axis.text.x = ggplot2::element_text(color = "black",
                                                          face = "bold",
                                                          angle = 0,
                                                          hjust = 0.5,
                                                          vjust = 1),
                      axis.text.x.top = ggplot2::element_text(color = "black",
                                                              face = "bold",
                                                              angle = 0,
                                                              hjust = 0.5,
                                                              vjust = 1),
                      axis.text.y = ggplot2::element_blank(),
                      axis.ticks = ggplot2::element_blank(),
                      panel.grid.major = ggplot2::element_blank(),
                      plot.title.position = "plot",
                      plot.title = ggplot2::element_text(face = "bold", hjust = 0),
                      plot.subtitle = ggplot2::element_text(hjust = 0),
                      plot.caption = ggplot2::element_text(hjust = 1),
                      panel.grid = ggplot2::element_blank(),
                      text = ggplot2::element_text(family = font.type),
                      plot.caption.position = "plot",
                      legend.text = ggplot2::element_text(face = "bold"),
                      legend.position = "none",
                      legend.title = ggplot2::element_text(face = "bold"),
                      legend.justification = "center",
                      plot.margin = ggplot2::margin(t = 10, r = 10, b = 10, l = 10),
                      plot.background = ggplot2::element_rect(fill = "white", color = "white"),
                      panel.background = ggplot2::element_rect(fill = "white", color = "white"),
                      legend.background = ggplot2::element_rect(fill = "white", color = "white"),
                      strip.text =ggplot2::element_text(color = "black", face = "bold"))

  return(p)
}
```

#### do_Table_Heatmap

`do_Table_Heatmap` shows heatmap of counts of cells in groups of metadata

- `data` seurat object 
- `first_group` is the name of the first metadata to group the cells
- `last_group` is the name of the second metadata to group the cells

```{r fig.width=10, fig.height=4, out.width='100%'}
do_Table_Heatmap <- function(data, first_group, last_group ){

  df <- data@meta.data %>%
  mutate_if(sapply(data@meta.data, is.character), as.factor)  %>% 
  group_by( !!sym(first_group), !!sym(last_group))%>% 
  summarise(Nb = n())

p <- ggplot(df, aes(x= !!sym(first_group), y = !!sym(last_group), fill = Nb)) +
   geom_tile() +
   scale_fill_viridis(discrete=FALSE)  +
   theme_bw() +
   theme(text = element_text(size = 20))

return(p)
}
```

### Load the pre-processed `Seurat` object
```{r load, message=FALSE, warning=FALSE}
# open the processed rds object
srat <- readRDS(file.path(result_dir, paste0("02b-fetal_kidney_label-transfer_",params$sample_id,".Rds")))
DefaultAssay(srat) <- "SCT"
```

@@

```{r fig.width=20, fig.height=4, out.width='100%'}
visualize_metadata(srat, meta = "Phase", group.by = "seurat_clusters")
```

```{r fig.width=20, fig.height=2.5, out.width='100%'}
visualize_metadata(srat, meta  = "S.Score", group.by = "seurat_clusters")
visualize_metadata(srat, meta = "G2M.Score", group.by = "seurat_clusters")
```

@@

```{r fig.width=20, fig.height=4, out.width='100%'}
for(feature in CellType_metadata$ENSEMBL_ID[CellType_metadata$ENSEMBL_ID %in% rownames(srat@assays$SCT)]){
   print(visualize_feature(srat, features = feature, group.by = "seurat_clusters"))
}
```

@@

```{r fig.height=4, fig.width=20, warning=FALSE, out.width='100%'}
srat <- MSigDB_score(object = srat , category = "H", gs_name = "HALLMARK_P53_PATHWAY", name = "TP53_score")
visualize_metadata(srat, meta = "TP53_score1", group.by = "seurat_clusters" )
```

@@

```{r fig.height=4, fig.width=20, warning=FALSE, out.width='100%'}
srat <- MSigDB_score(object = srat , category = "H", gs_name = "HALLMARK_DNA_REPAIR", name = "DNA_repair_score")
visualize_metadata(srat, meta = "DNA_repair_score1", group.by = "seurat_clusters" )
```

@@

```{r fig.height=4, fig.width=20, warning=FALSE, out.width='100%'}
srat <- MSigDB_score(object = srat , category = "C3", gs_name = "DROSHA_TARGET_GENES", name = "DROSHA_score")
visualize_metadata(srat, meta = "DROSHA_score1", group.by = "seurat_clusters" )
```

@@

```{r fig.height=4, fig.width=20, warning=FALSE, out.width='100%'}
srat <- MSigDB_score(object = srat , category = "C3", gs_name = "DICER1_TARGET_GENES", name = "DICER1_score")
visualize_metadata(srat, meta = "DICER1_score1", group.by = "seurat_clusters" )
```

@@

In addition to the list of known marker genes, we used an unbiased approach to find transcripts that characterized the different clusters.

We run DElegate::FindAllMarkers2 to find markers of the different clusters and manually check if they do make sense. 
DElegate::FindAllMarkers2 is an improved version of Seurat::FindAllMarkers based on pseudobulk differential expression method. 
Please check the preprint from Chistoph Hafemeister: https://www.biorxiv.org/content/10.1101/2023.03.28.534443v1
and tool described here: https://github.com/cancerbits/DElegate

@@

```{r fig.width=10, fig.height=10, out.width='100%'}
feature_conversion <- srat@assays$RNA@meta.data
de_results   <- DElegate::FindAllMarkers2(srat, group_column = "seurat_clusters")
#filter the most relevant markers
s.markers <- de_results[de_results$padj < params$padj_thershold & de_results$log_fc > params$lfc_threshold & de_results$rate1 > params$rate1_threshold,]
# add gene symbol for easiest interpretation of the result
s.markers$gene_ids <- s.markers$feature
s.markers <- left_join(s.markers,feature_conversion, by = c( "gene_ids") )
stopifnot(
  "Error joining gene ids and feature names" = identical(s.markers$feature, s.markers$gene_ids)   
)
```

```{r fig.width=10, fig.height=10, out.width='100%'}

DT::datatable(s.markers, caption = ("marker genes"), 
              extensions = 'Buttons', 
              options = list(  dom = 'Bfrtip',
                               buttons = c( 'csv', 'excel')))

```{r fig.width=10, fig.height=10, out.width='100%'}

# Select top 5 genes for heatmap plotting
s.markers <- na.omit(s.markers)
s.markers %>%
    group_by(group1) %>%
    top_n(n =  5, wt = log_fc) -> top5
# subset for plotting
cells <- WhichCells(srat, downsample = 100)
ss <- subset(srat, cells = cells)
ss <- ScaleData(ss, features = top5$feature)
p1 <- SCpubr::do_DimPlot(srat, reduction="umap", group.by = "seurat_clusters", label = TRUE, repel = TRUE) + ggtitle("Seurat Cluster - umap")
p2 <- DoHeatmap(ss, features = top5$feature,  cells = cells, group.by = "seurat_clusters") + NoLegend() + 
  scale_fill_gradientn(colors =  c("#01665e","#35978f",'darkslategray3', "#f7f7f7", "#fee391","#fec44f","#F9AD03")) 
p3 <- ggplot(srat@meta.data, aes(seurat_clusters, fill = seurat_clusters)) + geom_bar() + NoLegend()
common_title <- sprintf("Unsupervised clustering %s, %d cells", srat@meta.data$orig.ident[1], ncol(srat))
show((((p1 / p3) + plot_layout(heights = c(3,2)) | p2) ) + plot_layout(widths = c(1, 2)) + plot_layout(heights = c(3,1)) + plot_annotation(title = common_title))

```{r fig.width=10, fig.height=10, out.width='100%'}
DT::datatable(top5[, c(1, 9, 11, 12)], caption = ("top 5 marker genes"), 
              extensions = 'Buttons', 
              options = list(  dom = 'Bfrtip',
                               buttons = c( 'csv', 'excel')))

@@

```{r fig.width=20, fig.height=8, out.width='100%'}

@@

```{r fig.width=20, fig.height=10, out.width='100%'}
visualize_metadata(srat, meta = "singler_celltype_annotation", group.by = "seurat_clusters")
```

@@

```{r fig.width=20, fig.height=10, out.width='100%'}
visualize_metadata(srat, meta = "cellassign_celltype_annotation", group.by = "seurat_clusters")
```

@@

```{r fig.width=20, fig.height=10, out.width='100%'}
visualize_metadata(srat, meta = "fetal_full_predicted.organ", group.by = "seurat_clusters")
visualize_metadata(srat, meta = "fetal_full_predicted.annotation.l1", group.by = "seurat_clusters")
visualize_metadata(srat, meta = "fetal_full_predicted.annotation.l2", group.by = "seurat_clusters")
```

@@

```{r fig.width=20, fig.height=10, out.width='100%'}
visualize_metadata(srat, meta = "fetal_kidney_predicted.compartment", group.by = "seurat_clusters")
visualize_metadata(srat, meta = "fetal_kidney_predicted.cell_type", group.by = "seurat_clusters")
```

@@

```{r fig.width=20, fig.height=15, out.width='100%'}

@@

#### Sankey plots

```{r fig.width=20, fig.height=20, out.width='100%'}

p1 <- do_SankeyPlot(sample = srat,
                            first_group = "fetal_kidney_predicted.compartment",
                            last_group = "seurat_clusters",
                             type = "sankey",text_size = 5, use_labels = TRUE
                            )

p2 <- do_SankeyPlot(sample = srat,
                            first_group = "fetal_full_predicted.annotation.l1",
                            last_group = "seurat_clusters",
                             type = "sankey",text_size = 5, use_labels = TRUE
                            )

p3 <- do_SankeyPlot(sample = srat,
                            first_group = "singler_celltype_annotation",
                            last_group = "seurat_clusters",
                             type = "sankey",text_size = 4, use_labels = TRUE
                            )

p4 <- do_SankeyPlot(sample = srat,
                            first_group = "cellassign_celltype_annotation",
                            last_group = "seurat_clusters",
                             type = "sankey",text_size = 5, use_labels = TRUE
                            )

(p1|p2)/(p3|p4)
```

```{r fig.width=30, fig.height=10, out.width='100%'}
p1 <- do_SankeyPlot(sample = srat,
                            first_group = "fetal_kidney_predicted.compartment",
                            last_group = "fetal_full_predicted.annotation.l1",
                            type = "sankey",text_size = 6, use_labels = TRUE
 )

p2 <- do_SankeyPlot(sample = srat,
                            first_group = "fetal_kidney_predicted.compartment",
                            last_group = "fetal_kidney_predicted.cell_type",
                            type = "sankey",text_size = 6, use_labels = TRUE                                                        )

p1 | p2
```
#### Heatmaps

```{r fig.width=20, fig.height=15, out.width='100%'}
p1 <- do_Table_Heatmap( srat,
                            last_group = "fetal_kidney_predicted.compartment",
                            first_group = "seurat_clusters"

@@

p2 <- do_Table_Heatmap( srat,
                            last_group = "fetal_full_predicted.annotation.l1",
                            first_group = "seurat_clusters"
                            )

p3 <- do_Table_Heatmap( srat,
                            last_group = "singler_celltype_annotation",
                            first_group = "seurat_clusters"
                            )

p4 <- do_Table_Heatmap( srat,
                            last_group = "cellassign_celltype_annotation",
                            first_group = "seurat_clusters"
                            )

(p1|p2)/(p3|p4)
```
